|

### 2022-12-12 r-report/Paper.tex
zwischenstand

The question arises, how China plans to curb its emissions. At the
United Nations General Assembly in 2020, Chinese President Xi Jinping
announced the goal of Chinese carbon neutrality before 2060
\citep{Jinping2020}. This was the first time China officially committed
to a long-term emissions reductions goal \citep{CAT2022}. One year
later, in November 2021, ahead of COP26, China submitted its updated NDC
to the UNFCCC. Accordingly, the country plans to peak its carbon
emissions before 2030, decrease the carbon intensity of GDP by over 65\%
(relative to 2005), have around 25\% of non-fossil fuels in primary
energy consumption by 2030, increase the forest stock volume by six
billion cubic meters until 2030 and have 1,200 GW of wind and solar
power capacity installed by the same year \citep{China2022}. Although
some of these objectives are vague to some degree, and the emissions
reduction target is only a relative goal, the ambitions China has set
for itself are a marked improvement over the targets set out in the
previous 2016 NDC. Additionally, it is important to note that these
goals are unconditional and hence not relying on external climate
finance. China has adopted numerous policies to support its
international targets, such as the ``Working Guidance for Carbon Dioxide
Peaking and Carbon Neutrality'' and the ``Action Plan for Carbon Dioxide
Peaking Before 2030''. The former spells out a set of principles and
sectoral goals to achieve carbon dioxide peaking and carbon neutrality,
among them the need to exercise nationwide planning and the
prioritization of conversing energy \citep{DRCEP2021a}. The latter
defines key tasks for driving the low-carbon energy transition or saving
energy, carbon emission mitigation and efficiency improvement
\citep{DRCEP2021b}. With its ``14th Five-Year Plan on Renewable
Energy'', the country aims to further accelerate its renewable energy
expansion. By 2025, 33\% of electricity ought to be supplied by
renewable sources (18\% non-hydro), which could decrease annual carbon
emissions by 2.6 gigatons \citep{Zhou2022}.

@@

With these developments in mind and following up on China's claim to be
a developing country, we set out in this paper to discuss equity
considerations for China, focusing on two research questions. First, we
will investigate whether China, from an emissions perspective, can still
be characterized as a developing nation. For this we compare China's
Kaya identity with other developing and developed nations. Furthermore,
we consider China's sectoral emissions trends and contrast them with
those of (other) developing and developed nations, controlling for
differences in population size and GDP. Secondly, we investigate China's
claim of developed countries' being the driver of climate change, by
calculating different measures of (historic) responsibility and assess
the level of responsibility China bears in combatting climate change. We
discuss these findings with regards to a projection of China's
cumulative emissions.

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{Figure 1}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Figure 2}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Figure 3}
\end{figure}

@@

TO BE DONE FOrmula

@@

With a Kaya identity, one can identify the main driving forces of CO2
emissions in a certain period. The Kaya identity expresses CO2 emissions
(F) as a function of GDP (G), population (P) and energy (E):

TO BE DONE FOrmula

The term highlights the different components of the identity: G/P is GDP
per capita, E/G is the energy intensity of GDP and F/E is the carbon
intensity of energy \citep{Lamb2021}. By comparing Kaya identities of
different regions, we can also discuss regional differences. Hence, we
use the Kaya identity to discuss if the driving forces of emissions show
similarities with developing or developed nations.

@@

Comparing China's Kaya identity to the decomposition of the development
of CO2 emissions of developing and developed countries does not provide
a clear result on whether China can be considered a developing or
developed nation. In general, economic growth is the main driver of CO2
emissions, both in developed and developing nations. However, GDP per
capita growth is much larger and hence closer to China's figures in
developing nations as they show a greater growth potential. Overall
carbon emissions are decreasing in developed nations while they are
increasing in developing nations and China. This supports the notion of
China being a developing country relying on emissions driven growth. On
the other hand, China's energy and carbon intensity are decreasing as it
is the case for developed countries. The population's development of
China also more closely resembles the trend of developed countries than
those of developing countries. To sum up, this classification does not
clearly indicate whether China is a developing or developed country. As
mentioned above, comparing China to a more granular classification of
countries might be worthwhile, as the EDGAR dataset for example
considers Saudi-Arabia, a country with one of the highest GDP per capita
as a developing nation.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Figure 4}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Figure 5}
\end{figure}

@@

\hypertarget{discussion}{%
\subsubsection{Discussion}\label{discussion}}

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{Figure 10}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{Figure 11}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{Figure 12}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{Figure 13}
\end{figure}

\hypertarget{discussion-tbd}{%
\subsubsection{Discussion TBD}\label{discussion-tbd}}

To sum up, China has a very high responsibility to mitigate climate
change, even the highest responsibility of all countries when
considering some of the discussed equity metrics. Based on our
calculations, China is likely surpass the EU well before 2030 and the US
shortly after in 2032 in terms of cumulative emissions over all GHGs
from 1850 to 2019 and a modeling of emissions thereafter. The difference
in emissions from all GHGs to CO2 emissions highlights the importance to
extend the frame of historic respon

@@

However, we also need to consider that China only ranks on 81st. and
43rd place considering their GDP per capita and their emissions per
capita, respectively. This diminishes China's responsibility to some
extent, showing that the global community needs to grant space for
economic development to be fair. However, this economic development
should ideally be decoupled from a growth in emissions. If we look at
the per capita emissions of the countries that rank first, we see that
these are mostly very small and, from the perspective of absolute
emissions, less important countries. Although these countries might have
a high ability to pay from a per capita perspective, their overall
economic power is not high. The opposite is true for China. China ranks
first place in absolute emissions and GDP in 2019 with a great distance
to the following places.

@@

\hypertarget{discussion-and-conclusion-tbd}{%
\section{Discussion and Conclusion
TBD}\label{discussion-and-conclusion-tbd}}

@@

Our analysis of different equity metrics for the second research
question has shown that China not only has a huge responsibility to curb
emissions, but also the financial capability to do so. The country is
the world's largest emitter in annual and cumulative terms (based on our
data) and has the highest GDP of all countries. While it is important to
acknowledge further room for development, one cannot disregard the fact
that without significant emission reductions from China, any attempt to
stay within the temperature limits of the Paris Agreement is sure to
fail.

Hence, we believe that China's fair share is much higher than what they
currently plan to do. Together with the EU-27 and the U.S., China should
bear the highest responsibility for climate change mitigation. Its
self-classification as a developing country is clearly politically
motivated, to not give in to the demands of having to do more. At the
same time, the political leadership in Beijing can present itself as a
top student in the international community by effortlessly surpassing
its own goals, as it is expected by different observers \citep{CAT2022}.

In the following, our analysis will be contrasted with two other
assessments of China's fair share -- the assessment by the Climate
Action Tracker and by the Climate Equity Monitor.

@@

Another equity metric is developed by the Climate Equity Monitor. The
Climate Equity Monitor is the first initiative from the Global South
that tracks equity in climate action for Annex 1 and Non-Annex 1
countries. The initiative calculates the fair share of the carbon budget
by using the share of cumulative emissions based on the share in the
global population for a contemporary base year (2019). The cumulative
annual emissions of a country are calculated for the period from 1850 to
2019. Based on this, the Climate Equity Monitor calculates if a country
has a carbon debt or carbon credit. This measure is calculated as the
difference between cumulative emissions of a country and the country's
fair share of the global carbon budget already consumed. For China as a
Non-Annex 1 country, they conclude that the country has a carbon credit
of 122.4 Gt CO2eq. In comparison, India has a carbon credit of 337.6 Gt
CO2eq while the US has a carbon debt of 445 Gt CO2eq, and Russia has a
carbon debt of 125.44 Gt CO2eq \citep{CEM2022}. Accordingly, if China
kept emitting at its current rate, it would have used up its remaining
carbon credit until 2031.

@@

Our analysis has the following limitations: We only consider cumulative
emissions from 1850-2019, but the consideration of other time periods
could also be conceivable. The problem of climate change caused by
anthropogenic greenhouse gas emissions has only been known since the
1970s, and since the 1990s there has been a dedicated international
process to address the problem. Against this background, an additional
consideration of cumulative emissions in these time periods might be
worthwhile. For a comprehensive assessment of China's fair share, it
would have also been interesting to discuss further equity metrics such
as a ranking of consumption-based emissions. However, this was not
possible for us, as our data only included consumption-based data for
approx. 100 countries and crucially missing the US, making a comparison
less meaningful.

@@

\begin{itemize}\raggedright
  \item R version 4.2.1 (2022-06-23 ucrt), \verb|x86_64-w64-mingw32|
  \item Running under: \verb|Windows 10 x64 (build 22621)|
  \item Matrix products: default
  \item Base packages: base, datasets, graphics, grDevices, methods,
    stats, utils
  \item Other packages: dplyr~1.0.10, eurostat~3.7.10, forcats~0.5.2,
    ggplot2~3.3.6, ggridges~0.5.4, imputeTS~3.3, kableExtra~1.3.4,
    magrittr~2.0.3, openxlsx~4.2.5, pacman~0.5.1, plotly~4.10.1,
    purrr~0.3.4, readr~2.1.2, readxl~1.4.1, stringr~1.4.1,
    tibble~3.1.8, tidyr~1.2.1, tidyverse~1.3.2, WDI~2.7.8
  \item Loaded via a namespace (and not attached): assertthat~0.2.1,
    backports~1.4.1, bibtex~0.5.0, broom~1.0.1, cellranger~1.1.0,
    class~7.3-20, classInt~0.4-8, cli~3.4.0, colorspace~2.0-3,
    compiler~4.2.1, countrycode~1.4.0, crayon~1.5.1, curl~4.3.2,
    data.table~1.14.2, DBI~1.1.3, dbplyr~2.2.1, digest~0.6.29,
    e1071~1.7-11, ellipsis~0.3.2, evaluate~0.16, fansi~1.0.3,
    farver~2.1.1, fastmap~1.1.0, forecast~8.18, fracdiff~1.5-2,
    fs~1.5.2, gargle~1.2.1, generics~0.1.3, ggtext~0.1.2, glue~1.6.2,
    googledrive~2.0.0, googlesheets4~1.0.1, grid~4.2.1, gridtext~0.1.5,
    gtable~0.3.1, haven~2.5.1, here~1.0.1, highr~0.9, hms~1.1.2,
    htmltools~0.5.3, htmlwidgets~1.5.4, httr~1.4.4, jsonlite~1.8.0,
    KernSmooth~2.23-20, knitr~1.40, labeling~0.4.2, lattice~0.20-45,
    lazyeval~0.2.2, lifecycle~1.0.2, lmtest~0.9-40, lubridate~1.8.0,
    modelr~0.1.9, munsell~0.5.0, nlme~3.1-157, nnet~7.3-17,
    parallel~4.2.1, pillar~1.8.1, pkgconfig~2.0.3, plyr~1.8.7,
    proxy~0.4-27, quadprog~1.5-8, quantmod~0.4.20, R6~2.5.1,
    Rcpp~1.0.9, RefManageR~1.4.0, regions~0.1.8, reprex~2.0.2,
    rlang~1.0.5, rmarkdown~2.16, rprojroot~2.0.3, rstudioapi~0.14,
    rvest~1.0.3, scales~1.2.1, stinepack~1.4, stringi~1.7.8,
    svglite~2.1.0, systemfonts~1.0.4, tidyselect~1.1.2,
    timeDate~4021.104, tools~4.2.1, tseries~0.10-52, TTR~0.24.3,
    tzdb~0.3.0, urca~1.3-3, utf8~1.2.2, vctrs~0.4.1, viridisLite~0.4.1,
    webshot~0.5.3, withr~2.5.0, xfun~0.33, xml2~1.3.3, xts~0.12.2,
    yaml~2.3.5, zip~2.2.1, zoo~1.8-11
\end{itemize}

>>>>

The question arises, how China plans to curb its emissions. At the
United Nations General Assembly in 2020, Chinese President Xi Jinping
announced the goal of Chinese carbon neutrality before 2060
\citep{Jinping2020}. This was the first time China officially committed
to a long-term emissions reductions goal \citep{CAT2022}. One year
later, in November 2021, ahead of COP26, China submitted its updated NDC
to the UNFCCC. Accordingly, the country plans to peak its carbon
emissions before 2030, decrease the carbon intensity of GDP by over 65\%
(relative to 2005), have around 25\% of non-fossil fuels in primary
energy consumption by 2030, increase the forest stock volume by six
billion cubic meters until 2030 and have 1,200 GW of wind and solar
power capacity installed by the same year \citep{China2021}. Although
some of these objectives are vague to some degree, and the emissions
reduction target is only a relative goal, the ambitions China has set
for itself are a marked improvement over the targets set out in the
previous 2016 NDC. Additionally, it is important to note that these
goals are unconditional and hence not relying on external climate
finance. China has adopted numerous policies to support its
international targets, such as the ``Working Guidance for Carbon Dioxide
Peaking and Carbon Neutrality'' and the ``Action Plan for Carbon Dioxide
Peaking Before 2030''. The former spells out a set of principles and
sectoral goals to achieve carbon dioxide peaking and carbon neutrality,
among them the need to exercise nationwide planning and the
prioritization of conversing energy \citep{DRCEP2021a}. The latter
defines key tasks for driving the low-carbon energy transition or saving
energy, carbon emission mitigation and efficiency improvement
\citep{DRCEP2021b}. With its ``14th Five-Year Plan on Renewable
Energy'', the country aims to further accelerate its renewable energy
expansion. By 2025, 33\% of electricity ought to be supplied by
renewable sources (18\% non-hydro), which could decrease annual carbon
emissions by 2.6 gigatons \citep{Zhou2022}.

@@

With these developments in mind and following up on China's claim to be
a developing country, we set out in this paper to discuss equity
considerations for China, focusing on two research questions. First, we
will investigate whether China, from an emissions perspective, can still
be characterized as a developing nation. For this we compare China's
Kaya Identity with other developing and developed nations. Furthermore,
we consider China's sectoral emissions trends and contrast them with
those of (other) developing and developed nations, controlling for
differences in population size and GDP. Secondly, we investigate China's
claim of developed countries' being the driver of climate change, by
calculating different measures of (historic) responsibility and assess
the level of responsibility China bears in combatting climate change. We
discuss these findings with regards to a projection of China's
cumulative emissions.

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-1-1.pdf}
\caption{Figure 1: Relative Emissions of the Top- 5 Polluters}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-2-1.pdf}
\caption{Figure 2: Total Emissions, China by Sector - 1970-2019}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-3-1.pdf}
\caption{Figure 3: Kaya Identity China - 2000 - 2019}
\end{figure}

@@

\[\text{GNI} = \text{GDP} + \left (\text{EX}_{FS} - \text{IM}_{FS} \right )\]

whereas \(\text{GNI}\) be the gross national income, \(\text{GDP}\) be
the gross domestic product, \(\text{EX}_{FS}\) be the money flowing
from, and \(\text{IM}_{FS}\) the money flowing to foreign countries.

@@

With a Kaya Identity, one can identify the main driving forces of CO2
emissions in a certain period. The Kaya Identity expresses CO2 emissions
\(F\) as a function of GDP \(G\), population \(P\) and energy \(E\):

\[F = P \: \frac{G}{P} \frac{E}{G} \frac{F}{E}\]

whereas \(\frac{G}{P}\) represents GDP per capita, \(\frac{E}{G}\)
represents the energy intensity of GDP and \(\frac{F}{E}\) represents
the carbon intensity of energy \citep{Lamb2021}. By comparing Kaya
identities of different regions, we can also discuss regional
differences. Hence, we use the Kaya Identity to discuss if the driving
forces of emissions show similarities with developing or developed
nations.

@@

Comparing China's Kaya Identity to the decomposition of the development
of CO2 emissions of developing and developed countries does not provide
a clear result on whether China can be considered a developing or
developed nation. In general, economic growth is the main driver of CO2
emissions, both in developed and developing nations. However, GDP per
capita growth is much larger and hence closer to China's figures in
developing nations as they show a greater growth potential. Overall
carbon emissions are decreasing in developed nations while they are
increasing in developing nations and China. This supports the notion of
China being a developing country relying on emissions driven growth. On
the other hand, China's energy and carbon intensity are decreasing as it
is the case for developed countries. The population's development of
China also more closely resembles the trend of developed countries than
those of developing countries. To sum up, this classification does not
clearly indicate whether China is a developing or developed country. As
mentioned above, comparing China to a more granular classification of
countries might be worthwhile, as the EDGAR dataset for example
considers Saudi-Arabia, a country with one of the highest GDP per capita
as a developing nation.

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-4-1.pdf}
\caption{Figure 4: Kaya Identities - 2000 - 2019\textbar{} China
vs.~Developed and Developing according to AR\_6 Classification}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-5-1.pdf}
\caption{Figure 5:Kaya Identities - 2000 - 2019\textbar{} China
vs.~Developed and Developing according to AR\_6 Classification}
\end{figure}

@@

\hypertarget{section-summary}{%
\subsubsection{Section Summary}\label{section-summary}}

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{Figure 10: Absolute GHG Emission - 2019 \textbar{} Top
Emittters, China, US, EU-27 and reference for GDP, Emissions and
Population}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-11-1.pdf}
\caption{Figure 11: Per Capita Emissions- 2019 \textbar{} Top Emittters,
China, US, EU-27 and reference for GDP, Emissions and Population}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-12-1.pdf}
\caption{Figure 12: Absolute GDP p - 2019 \textbar{} Highes GDP
Countries, China, US, EU-27 and reference for GDP, Emissions and
Population}
\end{figure}

\begin{figure}
\centering
\includegraphics{Paper_files/figure-latex/unnamed-chunk-13-1.pdf}
\caption{Figure 13: GDP per Capita - 2019 \textbar{} Highes GDP
Countries, China, US, EU-27 and reference for GDP, Emissions and
Population}
\end{figure}

\hypertarget{section-summary-1}{%
\subsubsection{Section Summary}\label{section-summary-1}}

To sum up, China has a very high responsibility to mitigate climate
change, even the highest responsibility of all countries when
considering some of the discussed equity metrics. Based on our
calculations, China is likely to surpass the EU well before 2030 and the
US shortly after in 2032 in terms of cumulative emissions over all GHGs
from 1850 to 2019 and a modeling of emissions thereafter. The difference
in emissions from all GHGs to CO2 emissions highlights the importance to
extend the frame of historic responsibility beyond CO2 emissions --
especially in light of growing capabilities, issue salience and data
availability that all put greater responsibility recent emissions.

@@

However, we also need to consider that China only ranks on 81st and 43rd
place considering their GDP per capita and their emissions per capita,
respectively. This diminishes China's responsibility to some extent,
showing that the global community needs to grant space for economic
development to be fair. However, this economic development should
ideally be decoupled from a growth in emissions. If we look at the per
capita emissions of the countries that rank first, we see that these are
mostly very small and, from the perspective of absolute emissions, less
important countries. Although these countries might have a high ability
to pay from a per capita perspective, their overall economic power is
not high. The opposite is true for China. China ranks first place in
absolute emissions and GDP in 2019 with a great distance to subsequent
ranks.

@@

\hypertarget{discussion-and-conclusion}{%
\section{Discussion and Conclusion}\label{discussion-and-conclusion}}

@@

Our analysis of different equity metrics for the second research
question has shown that China not only has a huge responsibility to curb
emissions, but also the financial capability to do so. The country is
the world's largest emitter in annual terms , on a pathway to take the
first position in cumulative terms within a decade and has the highest
GDP of all countries. While it is important to acknowledge the need for
further economic development, one cannot disregard the fact that without
significant emission reductions from China, any attempt to stay within
the temperature limits of the Paris Agreement is sure to fail.

Hence, we believe that China's fair share is much higher than what they
currently plan to do. Together with the EU-27 and the U.S., China should
bear the highest responsibility for climate change mitigation. Its
self-classification as a developing country is clearly politically
motivated, to not give-in to the demands of raising its ambition. At the
same time, the political leadership in Beijing can present itself as a
top student in the international community by effortlessly surpassing
its own goals, as it is expected by different observers \citep{CAT2022}.

In the following, our analysis will be contrasted with two other
assessments of China's responsibility -- the assessment by the Climate
Action Tracker and by the Climate Equity Monitor.

@@

Another equity metric is developed by the Climate Equity Monitor. The
Climate Equity Monitor is the first initiative from the Global South
that tracks equity in climate action for Annex 1 and Non-Annex 1
countries. The initiative calculates the fair share of the carbon budget
by using the share of cumulative emissions based on the share in the
global population for a contemporary base year (2019). The cumulative
annual emissions of a country are calculated for the period from 1850 to
2019. Based on this, the Climate Equity Monitor calculates whether a
country has a carbon debt or carbon credit. This measure is calculated
as the difference between cumulative emissions of a country and the
country's fair share of the global carbon budget already consumed. For
China as a Non-Annex 1 country, they conclude that the country has a
carbon credit of 122.4 Gt CO2eq. In comparison, India has a carbon
credit of 337.6 Gt CO2eq while the US has a carbon debt of 445 Gt CO2eq,
and Russia has a carbon debt of 125.44 Gt CO2eq \citep{CEM2022}.
Accordingly, if China kept emitting at its current rate, it would have
used up its remaining carbon credit until 2031.

@@

While aiming to be as comprehensive as possible our analysis has some
limitations. First, we only consider cumulative emissions from
1850-2019, but the consideration of other time periods could also be
conceivable. The problem of climate change caused by anthropogenic
greenhouse gas emissions has only been known since the 1970s, and since
the 1990s there has been a dedicated international process to address
the problem. Against this background, an additional consideration of
cumulative emissions in these time periods might be worthwhile. Second,
the projection of future emissions rests on major simplification
assumptions, it is likely that a more sophisticated approach such as an
ARIMA-modelling would result in more robust estimates. Third, a
comprehensive assessment of China's responsibility could discuss further
equity metrics such as a ranking of consumption-based emissions.
However, this was not possible for us, as our data only included
consumption-based data for approx. 100 countries and crucially missing
the US, making a comparison less meaningful. Lastly, reducing capacity
to mere GDP and GDP per capita considerations is very much simplifying
the issue, as land area, access to renewable resources and intellectual
property and many other factors determine a countries mitigation
potential, which is very likely to differ by sector.

With these limitations in mind, we believe none the less that our
analysis has shed light on the special case of China and has shown that
the under complex self-assessment does not withstand a thorough
analysis. Keeping these assessments in mind will be worthwhile when
assessing the responsibilities of upcoming developing nations. The case
of China has shown that it is crucial to come to a mutual understanding
of what constitutes responsibilities and how they can assessed on an
objective basis. Especially our analysis of future cumulative emissions
indicates that it will be key to frame the issue beyond CO2.

@@

\begin{itemize}\raggedright
  \item R version 4.2.1 (2022-06-23 ucrt), \verb|x86_64-w64-mingw32|
  \item Running under: \verb|Windows 10 x64 (build 22621)|
  \item Matrix products: default
  \item Base packages: base, datasets, graphics, grDevices, methods,
    stats, utils
  \item Other packages: dplyr~1.0.10, eurostat~3.7.10, forcats~0.5.2,
    ggplot2~3.3.6, ggridges~0.5.4, imputeTS~3.3, kableExtra~1.3.4,
    magrittr~2.0.3, openxlsx~4.2.5, pacman~0.5.1, plotly~4.10.1,
    purrr~0.3.4, readr~2.1.2, readxl~1.4.1, stringr~1.4.1,
    tibble~3.1.8, tidyr~1.2.1, tidyverse~1.3.2, WDI~2.7.8
  \item Loaded via a namespace (and not attached): assertthat~0.2.1,
    backports~1.4.1, bibtex~0.5.0, broom~1.0.1, cellranger~1.1.0,
    class~7.3-20, classInt~0.4-8, cli~3.4.0, colorspace~2.0-3,
    compiler~4.2.1, countrycode~1.4.0, crayon~1.5.1, curl~4.3.2,
    data.table~1.14.2, DBI~1.1.3, dbplyr~2.2.1, digest~0.6.29,
    e1071~1.7-11, ellipsis~0.3.2, evaluate~0.16, fansi~1.0.3,
    farver~2.1.1, fastmap~1.1.0, forecast~8.18, fracdiff~1.5-2,
    fs~1.5.2, gargle~1.2.1, generics~0.1.3, ggtext~0.1.2, glue~1.6.2,
    googledrive~2.0.0, googlesheets4~1.0.1, grid~4.2.1, gridtext~0.1.5,
    gtable~0.3.1, haven~2.5.1, here~1.0.1, highr~0.9, hms~1.1.2,
    htmltools~0.5.3, htmlwidgets~1.5.4, httr~1.4.4, jsonlite~1.8.0,
    KernSmooth~2.23-20, knitr~1.40, labeling~0.4.2, lattice~0.20-45,
    lazyeval~0.2.2, lifecycle~1.0.2, lmtest~0.9-40, lubridate~1.8.0,
    modelr~0.1.9, munsell~0.5.0, nlme~3.1-157, nnet~7.3-17,
    parallel~4.2.1, pillar~1.8.1, pkgconfig~2.0.3, plyr~1.8.7,
    proxy~0.4-27, quadprog~1.5-8, quantmod~0.4.20, R6~2.5.1,
    RColorBrewer~1.1-3, Rcpp~1.0.9, RefManageR~1.4.0, regions~0.1.8,
    reprex~2.0.2, rlang~1.0.5, rmarkdown~2.16, rprojroot~2.0.3,
    rstudioapi~0.14, rvest~1.0.3, scales~1.2.1, stinepack~1.4,
    stringi~1.7.8, svglite~2.1.0, systemfonts~1.0.4, tidyselect~1.1.2,
    timeDate~4021.104, tools~4.2.1, tseries~0.10-52, TTR~0.24.3,
    tzdb~0.3.0, urca~1.3-3, utf8~1.2.2, vctrs~0.4.1, viridisLite~0.4.1,
    webshot~0.5.3, withr~2.5.0, xfun~0.33, xml2~1.3.3, xts~0.12.2,
    yaml~2.3.5, zip~2.2.1, zoo~1.8-11
\end{itemize}
